Restrictive Clearance Comparison

### 2024-08-16 data-raw/RestrictiveClearance_comparison.Rmd
Added new method twofold_test, updated manuscript vignette and a few methods. Notably, rsq

# Test which analyte_dtxsid don't have a clearance or vdist

data.frame(Chemical = unique(cvt$analyte_dtxsid)) %>%
  rowwise() %>%
  mutate(needs_RestCL = ifelse(
    (class(try(calc_total_clearance(dtxsid = Chemical,
                     restrictive.clearance = TRUE,
                     suppress.messages = TRUE))) == "try-error"),
    TRUE, FALSE),
    needs_nonRestCL = ifelse(
      (class(try(calc_total_clearance(dtxsid = Chemical,
                     restrictive.clearance = FALSE,
                     suppress.messages = TRUE))) == "try-error"),
    TRUE, FALSE),
    needs_Vdist = ifelse(
      (class(try(calc_vdist(dtxsid = Chemical,
                     suppress.messages = TRUE))) == "try-error"),
    TRUE, FALSE)) %>%
  ungroup() -> has_all_needed_df

@@

# Preliminary viz, plot all clearances
combined_clearance_df %>%
  relocate(CLtot.nca_mean, CLtot.nca_sd, .after = tidyselect::last_col()) %>%
  pivot_longer(cols = 3:6,
               names_to = "Clearance_Source",
               values_to = "Value") %>%
  ggplot(aes(x = Value,
             y = Chemical,
             fill = Clearance_Source)) +
  geom_point(shape = 21, alpha = 0.7) +
  scale_x_log10() +
  scale_fill_manual(breaks = c("nonRestrict_Cl", "CLtot.tkstats",
                               "CLtot.nca_mean",
                               "Restrict_Cl"),
                    labels = c("non-restrictive clearance (httk)",
                               "predicted clearance (invivoPKfit)",
                               "mean non-compartmental total clearance (invivoPKfit)",
                               "restrictive clearance (httk)"),
                    values = c("orange2", "grey5", "skyblue3",  "green4")) +
  facet_grid(rows = vars(Species), scales = "free", space = "free") +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        legend.position = "bottom",
        legend.direction = "vertical",
        axis.ticks = element_blank(),
        axis.line = element_blank())

@@

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_1comp", "model_1comp_cl_rest", "model_1comp_cl_nonrest"))
new_pk <- do_data_info(new_pk)

new_pk <- do_prefit(new_pk)

new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "Clint") %>%
  View()

new_pk <- do_fit(new_pk) # For troubleshooting only

@@

# Multidplyr error because of forgotten browser() call within log_likelihood
new_pk$fit %>% unnest(fit) %>% select(!starts_with("sigma_")) %>% View()

>>>>

# Test which analyte_dtxsid don't have a clearance or vdist
data.frame(Chemical = unique(cvt$analyte_dtxsid)) %>%
  rowwise() %>%
  mutate(needs_RestCL = ifelse(
    (class(try(calc_total_clearance(dtxsid = Chemical,
                     restrictive.clearance = TRUE,
                     suppress.messages = TRUE))) == "try-error"),
    TRUE, FALSE),
    needs_nonRestCL = ifelse(
      (class(try(calc_total_clearance(dtxsid = Chemical,
                     restrictive.clearance = FALSE,
                     suppress.messages = TRUE))) == "try-error"),
    TRUE, FALSE),
    needs_Vdist = ifelse(
      (class(try(calc_vdist(dtxsid = Chemical,
                     suppress.messages = TRUE))) == "try-error"),
    TRUE, FALSE)) %>%
  ungroup() -> has_all_needed_df

@@

# Preliminary viz, plot all clearances
combined_clearance_df %>%
  relocate(CLtot.nca_mean, CLtot.nca_sd, .after = tidyselect::last_col()) %>%
  pivot_longer(cols = 3:6,
               names_to = "Clearance_Source",
               values_to = "Value") %>%
  ggplot(aes(x = Value,
             y = Chemical,
             fill = Clearance_Source)) +
  geom_point(shape = 21, alpha = 0.7) +
  scale_x_log10() +
  scale_fill_manual(breaks = c("nonRestrict_Cl", "CLtot.tkstats",
                               "CLtot.nca_mean",
                               "Restrict_Cl"),
                    labels = c("non-restrictive clearance (httk)",
                               "predicted clearance (invivoPKfit)",
                               "mean non-compartmental total clearance (invivoPKfit)",
                               "restrictive clearance (httk)"),
                    values = c("orange2", "grey5", "skyblue3",  "green4")) +
  facet_grid(rows = vars(Species), scales = "free", space = "free") +
  labs(x = "Total Clearance") +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        legend.position = "bottom",
        legend.direction = "vertical",
        axis.ticks = element_blank(),
        axis.line = element_blank())

@@

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  scale_time(new_units = "auto") +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_1comp", "model_1comp_cl_rest", "model_1comp_cl_nonrest"))
new_pk <- do_data_info(new_pk)

new_pk <- new_pk + settings_optimx(method = c("bobyqa"))
new_pk <- do_prefit(new_pk)

unique(new_pk$prefit$par_DF$param_name)
new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "Fup") %>%
  View()

@@

new_pk$fit %>% unnest(fit) %>% select(!starts_with("sigma_")) %>% View()
